### 2004-07-15 Documentation/part1.tex
*** empty log message ***

\begin{table}[tpb]
\begin{center}
\begin{tabular}{p{3.8cm}p{3.8cm}p{7cm}}
\hline
Function & Purpose & Parameters \ra\ Result \\
\hline
\multicolumn{3}{l}{{\bf Systematics only:}} \\
\GLB{ChiSys} & $\chi^2$ with systematics only  & ({\tt glb\_params in, int exp, int rule}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projections onto axes:}} \\
\GLB{ChiTheta} & Projection onto $\theta_{13}$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDelta} & Projection onto $\deltacp$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiTheta23} & Projection onto $\theta_{23}$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDm} & Projection onto $\ldm$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDms} & Projection onto $\sdm$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projection onto plane:}} \\
\GLB{ChiThetaDelta} & Projection onto $\theta_{13}$-$\deltacp$-plane  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projection onto any hyper-plane:}} \\
\GLB{ChiNP} & Projection onto any $n$-dimensional hyper-plane  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \newline
Needs \GLB{SetProjection} before! \\[0.2cm]
\multicolumn{3}{l}{{\bf Localization of degeneracies:}} \\
\GLB{ChiAll} & (Local) Minimization over all parameters  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\
\hline
\end{tabular}
\end{center}
\caption{\label{tab:stdfunctions} \index{norm}{Standard functions (table)} The \GLOBES\ standard function to obtain a $\chi^2$-value with systematics only or systematics and correlations. The parameters {\tt rule} and {\tt exp}
can either be \GLBC{GLB\_ALL} for all initialized experiment or the
experiment number ($0$ to \GLB{\_num\_of\_exps}-1) for a specific experiment. The format of \GLB{\_params} is discussed in detail in \Chapt~\ref{chapt:gettingstarted}. Note that all functions but {\tt ChiSys}
  are using minimizers which have to be initialized with \GLB{SetInputErrors} and \GLB{SetStartingValues} first.}
\end{table}

@@

experiments. Note that a minimum at a negative value of $\theta_{13}$ is unphysical. However, if there can be no degeneracy found at a positive value, there is probably none at a low confidence level.  

@@

\index{norm}{Experiment!number of}
In principle, the \GLOBES\ user interface can currently handle up to 32 of different long-baseline experiments simultaneously, where the number
of existing experiment definition files can, of course, be unlimited. This means that their $\Delta \chi^2$-values are added {\em after} the minimization over the systematics parameters, and {\em before} any minimization over the oscillation parameters. Note that each experiment
assumes a specific matter density profile for all of its rules, which means
that it makes sense to simulate different operation modes within one
experiment definition, and physically different baselines in different
definitions. For details of the rate computation and
simulation techniques, we refer at this place to \Part~\ref{part:2}. Though
 the simplest case of simulating one experiment may be most often used, 
 using more than one experiments are useful in many cases. For example, combinations of experiments can be tested for
complementarity and competitiveness by equal means within one program.
In general, many \GLOBES\ functions take the experiment number as
a parameter, which runs from $0$ to \GLB{\_num\_of\_exps}-1 in the order of their initialization in the program.\footnote{Note that
the global variable {\tt glb\_num\_of\_exps} must not be modified by the
user.} In addition, using the parameter value \GLBC{GLB\_ALL} as
experiment number initiates a combined analysis of all loaded experiments.

@@

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in mega watts (superbeams), or thermal
 reactor power in giga watts (reactor experiments).
%
Since the pre-defined experiments in \tabl{experiments} are given for specific luminosities, it is useful to read out and change these
 parameters of the individual experiments:
\begin{function}
\GLBNS{SetSourcePower}
{\tt void glbSetSourcePower(double power, int exp, int fluxno)}
 sets the source power of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt power}. The definition of the source power depends on the experiment type as described above.
\end{function}
\begin{function}
\GLBNS{GetSourcePower}
{\tt double glbGetSourcePower(int exp, int fluxno)}
 returns the source power of experiment number {\tt exp} and flux number
 {\tt fluxno}. 
\end{function}
\begin{function}
\GLBNS{SetRunningTime}
{\tt void glbSetRunningTime(double time, int exp, int fluxno)}
 sets the running time of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt time} years.
\end{function}
\begin{function}
\GLBNS{GetRunningTime}
{\tt double glbGetRunningTime(int exp, int fluxno)}
 returns the running time of experiment number {\tt exp} and flux number
 {\tt fluxno}.
\end{function}
\begin{function}
 \GLBNS{SetTargetMass}
{\tt void glbSetTargetMass(double mass,int exp)}
sets the fiducial detector mass of experiment number {\tt exp} to {\tt mass} tons or kilotons (depending on the experiment definition).
\end{function}
\begin{function}
 \GLBNS{GetTargetMass}
{\tt double glbGetTargetMass(int exp)}
returns the fiducial detector mass of experiment number {\tt exp}.
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number and others. These numbers run from $0$ to the number of experiments-1, fluxes-1, \etc, where the individual elements are numbered in the order of their appearance. 
 Note that the source power and running time are quantities defined
together with the neutrino flux, whereas the target mass scales the whole
experiment.

@@

Similarly, the density parameters or iterations can be accessed:
\begin{function}
\GLBNS{SetDensityParams}
{\tt glb\_params glbSetDensityParams(glb\_params in, double dens, int which)} sets the density parameter {\tt which} in the structure {\tt in}
to the value {\tt dens}. If the assignment was unsuccessful, the 
function returns {\tt NULL}. If {\tt GLB\_ALL} is used for {\tt which},
the density parameters of all experiments will be set accordingly.
\end{function}
\begin{function}
\GLBNS{GetDensityParams}
{\tt double glbGetDensityParams(glb\_params in, int which)}
returns the value of the density parameter {\tt which} in the 
structure {\tt in}.
\end{function} 
\begin{function}
\GLBNS{SetIteration} \index{norm}{Iterations}
{\tt glb\_params glbSetIteration(glb\_params in, int iter)} sets the number of iterations in the structure {\tt in}
to the value {\tt iter}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{GetIteration}
{\tt int glbGetIteration(glb\_params in)}
returns the value of the number of iterations in the 
structure {\tt in}.
\end{function}
In total, the parameter vector handling in a program normally has the
following order:\index{norm}{Parameter vector handling}
\begin{quote}
{\tt
glbInitExperiment(...); \\
/* ... more initializations ... */ \\
\\
glb\_params vector1 = glbAllocParams(); \\
/* ... more vectors allocated ... */ \\
\\
/* Program code: assign and use vectors */ \\
\\
glbFreeParams(vector1); \\
/* ... more vectors destroyed ... */ \\
\\
/* ... end of program or glbClearExperimentList ... */ 
}
\end{quote}

@@

The functions in \GLOBES\ for version control are:
\begin{function}
\GLBNS{TestReleaseVersion}
{\tt int glbTestReleaseVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is older, and $-1$ if it is newer. 
\end{function}
\begin{function}
\GLBNS{TestLibraryVersion}
{\tt int glbTestLibraryVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is older, and $-1$ if it is newer.
Note that the library and \GLOBES\ versions are not the same. 
\end{function}
\begin{function}
\GLBNS{TestLibraryVersion}
{\tt int glbTestLibraryVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is older, and $-1$ if it is newer.
Note that the library and \GLOBES\ versions are not the same. 
\end{function}
\begin{function}
\GLBNS{VersionOfExperiment} 
{\tt const char* glbVersionOfExperiment(int experiment)} returns
the version string of the experiment number {\tt experiment}.
The version string points to the experiment structure, which means
that it cannot be altered and does not have to be destroyed by the
user.
\end{function}

@@

\index{norm}{Projection of manifold}
In principle, the precision of an individual parameter measurement including correlations in the $\chi^2$-approach can be obtained as the projection of the $n$-dimensional fit manifold onto the respective axis. Similarly, one can project the fit manifold onto a plane, such as the $\stheta$-$\deltacp$-plane, if one wants to explicitely show the allowed
region in this plane with all the other parameter correlations included. 
In practice, this projection is very difficult: a grid-based method would need $(N_{\mathrm{grid}})^n$ function calls of {\tt glbChiSys} to calculate the precision including the full $n$-parameter correlation, where $N_{\mathrm{grid}}$ is the number of points in each direction of the lattice. For example, taking only $N_{\mathrm{grid}}=20$ and $n=7$ (six oscillation parameters and matter density) would mean more than one billion function calls of {\tt glbChiSys}. One can easily image that this is too much for any sophisticated application.

@@

In principle, one can set the priors for the matter density and all oscillation parameters. For example, if the disappearance channels of the experiment determine the leading oscillation parameters with unprecedented
precisions, one can omit the respective input errors. In \GLOBES , a
value of $0$ corresponds to neglecting the prior. If, however, earlier external measurements provide better information, one can set their absolute precisions with the input errors. The starting values are usually chosen to be the best-fit values of this external input, such as
for the precisions of the solar experiments. In some cases, it may be
necessary to adjust them, such as for artificial constraints to the
oscillation parameters. In other cases, minor modifications of the starting values can cause a faster convergence of the algorithm.
For example, for the investigation of the
opposite-sign solution, one can use the prior to constrain $\ldm$
in order to force the minimizer not to  fall into the (unwanted) best-fit solution. In this case, the starting value of $\ldm$ would be set to $\rho^0_{\ldm} = - \ldm$, and a $\sigma_{\ldm}$ of the order of $\ldm$ would be imposed. For the algorithm, it would then be rather difficult 
to converge into the unwanted best-fit solution. However, note that one should in this case check that the actually determined value for $\ldm$ after minimization is close enough to the guessed values $-\ldm$ in order to avoid significant artifical contributions of the priors to the 
final $\chi^2$.

@@

\begin{quote}
{\tt {\scriptsize
  /* Set starting values and input errors for all projections */  \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,0);\\  
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL);\\
  glbSetStartingValues(true\_values);\\
  glbSetInputErrors(input\_errors);\\
\\
  /* Define two-parameter projection: Only deltacp is free! */ \\
  glbDefineProjection(th13\_projection,GLB\_FIXED,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FIXED,GLB\_FIXED); \\
  glbSetProjection(th13\_projection); \\ 
\\
  /* Iteration over all values to be computed */ \\
  double x,res1,res2;     \\
  for(x=-4;x<-2.0+0.001;x=x+2.0/50) \\
  \{ \\
\hspace*{0.5cm}  /* Set fit value of stheta */ \\
\hspace*{0.5cm} glbSetOscParams(test\_values,asin(sqrt(pow(10,x)))/2,1); \\
    \\
\hspace*{0.5cm} /* Guess fit value for deltacp in order to safely find minimum */ \\
\hspace*{0.5cm} glbSetOscParams(test\_values,200.0/2*(x+4)*M\_PI/180,3); \\
 \\
\hspace*{0.5cm} /* Compute Chi2 for user-defined two-parameter correlation */ \\
\hspace*{0.5cm} res1=glbChiNP(test\_values,NULL,GLB\_ALL); \\
      \\
\hspace*{0.5cm} /* Compute Chi2 for full correlation: minimize over all but theta13 */ \\
\hspace*{0.5cm} res2=glbChiTheta(test\_values,NULL,GLB\_ALL); \\
  \\
\hspace*{0.5cm} AddToOutput(x,res1,res2);\\
  \} \\

@@

\index{norm}{Matter density scaling factor}
The the output of the minimizer in {\tt out} carries as many matter density scaling factors as there are experiments. Either
one (for the simulation of one experiment) or all (for the simulation of
all experiments) are different from $1.0$ if matter density uncertainties
are present, since each experiment may face other matter density conditions. The minimizer for individual experiments ``know'' which
experiment they are currently treating, which means that only the returned
matter density scaling factor of the appropriate experiment is modified.
For example, calculating {\tt glbChiTheta} for the last experiment
number, the last density values will be modified.
This approach turns out to be extremely useful together with the
simulation of more than one experiment. One can, for instance, locate the
degeneracies of all individual experiments. In order to test if
these degeneracies are still present in the combination of all experiments (which has a very different topology), one can test the combination of experiments with the output {\tt out} from the individual experiments. In this case, even the correct matter density scaling factor
output is used.

@@

In the last chapter, we introduced the projection of any set of $k$ parameter onto any $n-k$ dimensional hyperplane, which was done by the minimization over the $k$ free fit parameters. Similarly, one can minimize over {\em all} $n$ parameters to find the local minimum close to any starting point. This approach is very useful for the exact numerical location of a degeneracy if its approximate position is known. For the determination of the approximate position, one can use analytical approaches or an educated guess. 
Though the usage of the all-parameter minimizers is quite simple, one should keep in mind that they are local minimizers. Therefore, one may need a very sophisticated application software to find all degenerate solutions.

@@

In many cases, one can find the exact position of the $\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and let it converge into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(starting\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetStartingValues(starting\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(starting\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}

@@

The example on page~\pageref{ex:sgndeg} illustrates how to locate the $\mathrm{sgn}(\ldm)$-degeneracy and show the corresponding degenerate solution in the $\stheta$-$\deltacp$-plane together with the original solution.
In this case, the position of the degeneracy can be easily guessed to be at the best-fit parameter values but the $\ldm$ inverted. The minimizer then runs off the plane of the best-fit parameters into the local minimum. It is very important to take into account the position of the degeneracy off this plane, since the actual $\chi^2$ in the minimum is certainly lower than on the plane of the best-fit parameter values. Thus, the degeneracy may not even appear at the chosen confidence level on the plane, but it does appear at the true minimum. The two sections\footnote{The discussed figure on page~\pageref{ex:sgndeg} is produced by  {\tt glbChiSys} and thus only represents a section through the fit manifold. For the projection including correlations, one may rather want to use {\tt glbChiThetaDelta}.} through the fit manifold shown in the figure on page~\pageref{ex:sgndeg} therefore do not appear at the same oscillation parameter values (except from the ones shown in the figure).

>>>>

\begin{table}[tpb]
\begin{center}
\begin{tabular}{p{3.8cm}p{3.8cm}p{7cm}}
\hline
Function & Purpose & Parameters \ra\ Result \\
\hline
\multicolumn{3}{l}{{\bf Systematics only:}} \\
\GLB{ChiSys} & $\chi^2$ with systematics only  & ({\tt glb\_params in, int exp, int rule}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projections onto axes:}} \\
\GLB{ChiTheta} & Projection onto $\theta_{13}$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDelta} & Projection onto $\deltacp$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiTheta23} & Projection onto $\theta_{23}$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDm} & Projection onto $\ldm$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.1cm]
\GLB{ChiDms} & Projection onto $\sdm$-axis  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projection onto plane:}} \\
\GLB{ChiThetaDelta} & Projection onto $\theta_{13}$-$\deltacp$-plane  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\[0.2cm]
\multicolumn{3}{l}{{\bf Projection onto any hyper-plane:}} \\
\GLB{ChiNP} & Projection onto any $n$-dimensional hyper-plane  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \newline
Needs \GLB{SetProjection} before! \\[0.2cm]
\multicolumn{3}{l}{{\bf Localization of degeneracies:}} \\
\GLB{ChiAll} & (Local) Minimization over all parameters  &  ({\tt glb\_params in, glb\_params out, int exp}) \ra\  {\tt double} $\chi^2$ \\
\hline
\end{tabular}
\end{center}
\caption{\label{tab:stdfunctions} \index{norm}{Standard functions (table)} The \GLOBES\ standard function to obtain a $\chi^2$-value with systematics only or systematics and correlations. The parameters {\tt rule} and {\tt exp}
can either be \GLBC{GLB\_ALL} for all initialized experiment or the
experiment number ($0$ to \GLB{\_num\_of\_exps}-1) for a specific experiment. The format of \GLB{\_params} is discussed in detail in \Chapt~\ref{chapt:gettingstarted}. Note that all functions but {\tt glbChiSys} are using minimizers which have to be initialized with \GLB{SetInputErrors} and \GLB{SetStartingValues} first.}
\end{table}

@@

experiments.

@@

\index{norm}{Experiment!number of}
In principle, the \GLOBES\ user interface can currently handle up to 32 of different long-baseline experiments simultaneously, where the number
of existing experiment definition files can, of course, be unlimited. This means that their $\Delta \chi^2$-values are added {\em after} the minimization over the systematics parameters, and {\em before} any minimization over the oscillation parameters. Note that each experiment
assumes a specific matter density profile, which means
that it makes sense to simulate different operation modes within one
experiment definition, and physically different baselines in different
definitions. For details of the rate computation and
simulation techniques, we refer at this place to \Part~\ref{part:2}. Though
 the simplest case of simulating one experiment may be most often used, 
 using more than one experiments are useful in many cases. For example, combinations of experiments can be tested for
complementarity and competitiveness by equal means within one program.
In general, many \GLOBES\ functions take the experiment number as
a parameter, which runs from $0$ to \GLB{\_num\_of\_exps}-1 in the order of their initialization in the program.\footnote{Note that
the global variable {\tt glb\_num\_of\_exps} must not be modified by the
user.} In addition, using the parameter value \GLBC{GLB\_ALL} as
experiment number initiates a combined analysis of all loaded experiments.

@@

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in mega watts (superbeams), or thermal
 reactor power in giga watts (reactor experiments).
%
Since the pre-defined experiments in \tabl{experiments} are given for specific luminosities, it is useful to read out and change these
 parameters of the individual experiments:
\begin{function}
\GLBNS{SetSourcePower}
{\tt void glbSetSourcePower(double power, int exp, int fluxno)}
 sets the source power of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt power}. The definition of the source power depends on the experiment type as described above.
\end{function}
\begin{function}
\GLBNS{GetSourcePower}
{\tt double glbGetSourcePower(int exp, int fluxno)}
 returns the source power of experiment number {\tt exp} and flux number
 {\tt fluxno}. 
\end{function}
\begin{function}
\GLBNS{SetRunningTime}
{\tt void glbSetRunningTime(double time, int exp, int fluxno)}
 sets the running time of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt time} years.
\end{function}
\begin{function}
\GLBNS{GetRunningTime}
{\tt double glbGetRunningTime(int exp, int fluxno)}
 returns the running time of experiment number {\tt exp} and flux number
 {\tt fluxno}.
\end{function}
\begin{function}
 \GLBNS{SetTargetMass}
{\tt void glbSetTargetMass(double mass,int exp)}
sets the fiducial detector mass of experiment number {\tt exp} to {\tt mass} tons or kilotons (depending on the experiment definition).
\end{function}
\begin{function}
 \GLBNS{GetTargetMass}
{\tt double glbGetTargetMass(int exp)}
returns the fiducial detector mass of experiment number {\tt exp}.
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number and others. These numbers run from $0$ to the number of experiments-1, fluxes-1, \etc, where the individual elements are numbered in the order of their appearance. 
 Note that the source power and running time are quantities defined
together with the neutrino flux, whereas the target mass scales the whole
experiment. Thus, if one has, for instance, a neutrino and an antineutrino
running mode, one can scale them independently.

@@

Similarly, the density parameters or number of iterations 
(returned by the minimizers) can be accessed:
\begin{function}
\GLBNS{SetDensityParams}
{\tt glb\_params glbSetDensityParams(glb\_params in, double dens, int which)} sets the density parameter {\tt which} in the structure {\tt in}
to the value {\tt dens}. If the assignment was unsuccessful, the 
function returns {\tt NULL}. If {\tt GLB\_ALL} is used for {\tt which},
the density parameters of all experiments will be set accordingly.
\end{function}
\begin{function}
\GLBNS{GetDensityParams}
{\tt double glbGetDensityParams(glb\_params in, int which)}
returns the value of the density parameter {\tt which} in the 
structure {\tt in}.
\end{function} 
\begin{function}
\GLBNS{SetIteration} \index{norm}{Iterations}
{\tt glb\_params glbSetIteration(glb\_params in, int iter)} sets the number of iterations in the structure {\tt in}
to the value {\tt iter}. If the assignment was unsuccessful, the 
function returns {\tt NULL}.
\end{function}
\begin{function}
\GLBNS{GetIteration}
{\tt int glbGetIteration(glb\_params in)}
returns the value of the number of iterations in the 
structure {\tt in}.
\end{function}
In total, the parameter vector handling in a program normally has the
following order:\index{norm}{Parameter vector handling}
\begin{quote}
{\tt
glbInitExperiment(...); \\
/* ... more initializations ... */ \\
\\
glb\_params vector1 = glbAllocParams(); \\
/* ... more vectors allocated ... */ \\
\\
/* Program code: assign and use vectors */ \\
\\
glbFreeParams(vector1); \\
/* ... more vectors destroyed ... */ \\
\\
/* ... end of program or glbClearExperimentList ... */ 
}
\end{quote}

@@

The functions in \GLOBES\ for version control are:
\begin{function}
\GLBNS{TestReleaseVersion}
{\tt int glbTestReleaseVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is older, and $-1$ if it is newer. 
\end{function}
\begin{function}
\GLBNS{TestLibraryVersion}
{\tt int glbTestLibraryVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is older, and $-1$ if it is newer.
Note that the library and \GLOBES\ versions are not the same. 
\end{function}
\begin{function}
\GLBNS{VersionOfExperiment} 
{\tt const char* glbVersionOfExperiment(int experiment)} returns
the version string of the experiment number {\tt experiment}.
The version string is allocated within the experiment structure, which means
that it cannot be altered and must not be destroyed by the
user.
\end{function}

@@

\index{norm}{Projection of manifold}
In principle, the precision of an individual parameter measurement including correlations in the $\chi^2$-approach can be obtained as the projection of the $n$-dimensional fit manifold onto the respective axis. Similarly, one can project the fit manifold onto a plane, such as the $\stheta$-$\deltacp$-plane, if one wants to show the allowed
region in this plane with all the other parameter correlations included. 
In practice, this projection is very difficult: a grid-based method would need $(N_{\mathrm{grid}})^n$ function calls of {\tt glbChiSys} to calculate the precision including the full $n$-parameter correlation, where $N_{\mathrm{grid}}$ is the number of points in each direction of the lattice. For example, taking only $N_{\mathrm{grid}}=20$ and $n=7$ (six oscillation parameters and matter density) would mean more than one billion function calls of {\tt glbChiSys}. One can easily imagine that these
would be too many for any reasonable application.

@@

In principle, one can set the priors for the matter density and all oscillation parameters. For example, if the disappearance channels of the experiment determine the leading oscillation parameters with unprecedented
precisions, one can omit the respective input errors. In \GLOBES , a
value of $0$ corresponds to neglecting the prior. If, however, earlier external measurements provide better information, one can set their absolute precisions with the input errors. The starting values are usually chosen to be the best-fit values of this external input, such as
for the precisions of the solar experiments. In some cases, it may be
necessary to adjust them, such as for artificial constraints to the
oscillation parameters. In other cases, minor modifications of the starting values can cause a faster convergence of the algorithm.
For example, for the investigation of the
opposite-sign solution, one can use the prior to constrain $\ldm$
in order to force the minimizer not to  fall into the (unwanted) best-fit solution. In this case, the starting value of $\ldm$ would be set to $\rho^0_{\ldm} = - \ldm$, and a $\sigma_{\ldm}$ of the order of $\ldm$ would be imposed. For the algorithm, it would then be rather difficult 
to converge into the unwanted best-fit solution. However, note that one should in this case check that the actually determined value for $\ldm$ after minimization is close enough to the guessed value $-\ldm$ in order to avoid significant artifical contributions of the priors to the 
final $\chi^2$.

@@

\begin{quote}
{\tt {\scriptsize
  /* Set starting values and input errors for all projections */  \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,0);\\  
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL);\\
  glbSetStartingValues(true\_values);\\
  glbSetInputErrors(input\_errors);\\
\\
  /* Define my own two-parameter projection for glbChiNP: Only deltacp is free! */ \\
  glbDefineProjection(th13\_projection,GLB\_FIXED,GLB\_FIXED,GLB\_FIXED,GLB\_FREE,GLB\_FIXED,GLB\_FIXED); \\
  glbSetProjection(th13\_projection); \\ 
\\
  /* Iteration over all values to be computed */ \\
  double x,res1,res2;     \\
  for(x=-4;x<-2.0+0.001;x=x+2.0/50) \\
  \{ \\
\hspace*{0.5cm}  /* Set fit value of stheta */ \\
\hspace*{0.5cm} glbSetOscParams(test\_values,asin(sqrt(pow(10,x)))/2,1); \\
    \\
\hspace*{0.5cm} /* Guess fit value for deltacp in order to safely find minimum */ \\
\hspace*{0.5cm} glbSetOscParams(test\_values,200.0/2*(x+4)*M\_PI/180,3); \\
 \\
\hspace*{0.5cm} /* Compute Chi2 for user-defined two-parameter correlation */ \\
\hspace*{0.5cm} res1=glbChiNP(test\_values,NULL,GLB\_ALL); \\
      \\
\hspace*{0.5cm} /* Compute Chi2 for full correlation: minimize over all but theta13 */ \\
\hspace*{0.5cm} res2=glbChiTheta(test\_values,NULL,GLB\_ALL); \\
  \\
\hspace*{0.5cm} AddToOutput(x,res1,res2);\\
  \} \\

@@

\index{norm}{Matter density scaling factor}
The output of the minimizer in {\tt out} carries as many matter density scaling factors as there are experiments. Either
one (for the simulation of one experiment) or all (for the simulation of
all experiments) are different from $1.0$ if matter density uncertainties
are present, since each experiment may face other matter density conditions. The minimizers of individual experiments ``know'' which
experiment they are currently treating, which means that only the returned
matter density scaling factor of the appropriate experiment is modified.
For example, calculating {\tt glbChiTheta} for the last experiment
number, the last density value will be modified.
This approach turns out to be extremely useful together with the
simulation of more than one experiment. One can, for instance, locate the
degeneracies of all individual experiments. In order to test if
these degeneracies are still present in the combination of all experiments (which has a very different topology), one can test the combination of experiments with the output {\tt out} from the individual experiments. In this case, even the correct matter density scaling factor
output is used.

@@

In the last chapter, we introduced the projection of any set of $k$ parameters onto any $n-k$ dimensional hyperplane, which was performed by the minimization over the $k$ free fit parameters. Similarly, one can minimize over {\em all} $n$ parameters to find the local minimum close to any starting point. This approach is very useful for the exact numerical location of a degeneracy if its approximate position is known. For the determination of the approximate position, one can use analytical approaches or an educated guess. 
Though the usage of the all-parameter minimizers is quite simple, one should keep in mind that they are local minimizers. Therefore, one may need a very sophisticated application software to find all degenerate solutions.

@@

In many cases, one can find the exact position of the $\mathrm{sgn}(\ldm)$-degeneracy with \GLB{ChiAll}, where one starts 
the local minimizer at the suspected position 
and let it run into the minimum.  The following code excerpt  corresponds to finding the degenerate solution for the example on
  page~\pageref{ex:corrth13dcp}, and it is from {\tt example3.c}: 
\begin{quote}
{\tt
{\footnotesize
  /* Set starting vales to suspected position at opposite sign of ldm */ \\
  \mbox{glbDefineParams(starting\_values,theta12,theta13,theta23,deltacp,sdm,-ldm);} \\
  \\
  /* Set input errors for external input, where some information on ldm \\
   \hspace*{0.5cm} is imposed in order to avoid falling into the right-sign solution */ \\
  glbDefineParams(input\_errors,theta12*0.1,0,0,0,sdm*0.1,ldm/3); \\ 
  glbSetDensityParams(input\_errors,0.05,GLB\_ALL); \\
  \\
  glbSetStartingValues(starting\_values); \\
  glbSetInputErrors(input\_errors); \\
  \\
  /* Localize degenerate solution by minimization over all parameters */ \\
  double CL=glbChiAll(starting\_values,deg\_pos,GLB\_ALL); \\
   \\
  \mbox{/* Now: CL is the chi2 of the deg.~solution and deg\_pos the position */} 
}}
\end{quote}

@@

The example on page~\pageref{ex:sgndeg} illustrates how to locate the $\mathrm{sgn}(\ldm)$-degeneracy and show the corresponding degenerate solution in the $\stheta$-$\deltacp$-plane together with the original solution.
In this case, the position of the degeneracy can be easily guessed to be at the best-fit parameter values but the inverted $\ldm$. The minimizer then runs off the plane of these parameters into the local minimum. It is very important to take into account the position of the degeneracy off this plane, since the actual $\chi^2$ in the minimum is probably lower than on the plane of the best-fit parameter values. Thus, the degeneracy may not even appear at the chosen confidence level on the plane, but it does appear at the true minimum. The two sections through the fit manifold shown in the figure on page~\pageref{ex:sgndeg} therefore do not appear at the same oscillation parameter values (except from the ones shown in the 
figure).\footnote{The discussed figure on page~\pageref{ex:sgndeg} is produced by  {\tt glbChiSys} and thus only represents a section through the fit manifold. For the projection including correlations, one may rather want to use {\tt glbChiThetaDelta}.}
